### 2015-05-03 latex/phd_thesis.tex
Fix formatting

@@

@@

The second half of the thesis focuses on \emph{co-methylation}, the spatial dependence of DNA methylation. We demonstrate that previous analyses of co-methylation have been limited by inadequate data and analysis methods. This motivates a study of co-methylation from 40 whole-genome bisulfite-sequencing samples. These 40 samples represent a diverse range of tissues, from embryonic and induced pluripotent stem cells, through to somatic cells and tumours. Making use of software developed in the first half of the thesis, we explore different measures of co-methylation and relate these to one another. We identify genomic features that influence co-methylation and how it varies between different tissues.

@@

The data sets used in this thesis were provided by the investigators

\textbf{TODO}: List investigators.

For full details, please see Chapter \ref{chap:datasets}.\\\\

@@

Finally, and most of all, thank you to my parents, Gay and John, to my brothers, Jack, Luke and Daniel, and to my friends. Your support, love and encouragement kept me going.

@@

% 2 - 4 pages
\textbf{TODO}

>>>>

% To insert blank (unnumbered) page after title page http://tex.stackexchange.com/a/36881
\usepackage{afterpage}
\newcommand\blankpage{%
    \null
    \thispagestyle{empty}%
    \addtocounter{page}{-1}%
    \newpage}

@@

\blankpage

@@

The second half of the thesis focuses on \emph{co-methylation}, the spatial dependence of DNA methylation. We demonstrate that previous analyses of co-methylation have been limited by inadequate data and deficiencies in the statistical methods applied. This motivates a study of co-methylation from 40 whole-genome bisulfite-sequencing samples. These 40 samples represent a diverse range of tissues, from embryonic and induced pluripotent stem cells, through to somatic cells and tumours. Making use of software developed in the first half of the thesis, we explore different measures of co-methylation and relate these to one another. We identify genomic features that influence co-methylation and how it varies between different tissues.

@@

The datasets used in this thesis were provided by the investigators listed below.

Aaron Statham and Sue Clark, Garvan Institute of Medical Research. The \emph{EPISCOPE} dataset.

Several publicly available datasets were also used and are described in Chapter \ref{chap:datasets}.\\\\

@@

Finally, and most of all, thank you to my parents, Gay and John, to my brothers, Jack, Luke and Daniel, and to my friends. Your support, love, and encouragement kept me going.

@@
